---
title: "SeuratVisPro Tutorial"
author: "benben-miao"
date: "2025-12-02"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{SeuratVisPro Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 10.00,
  fig.height = 6.18)
```

# SeuratVisPro

## 1. Introduction

**SourceCode:** <https://github.com/benben-miao/SeuratVisPro/>

**Website API**: <https://benben-miao.github.io/SeuratVisPro/>

SeuratVisPro is an innovative visualization and diagnostic toolkit for Seurat v5. It provides cluster stability assessment, batch mixing diagnostics, marker atlas visualization, ligand–receptor directional scoring, gene trend plotting, dendrograms with similarity heatmaps, spatial overlays with non-spatial fallbacks, module score visualization, cell cycle views, and more. An optional bs4Dash Shiny app is bundled for interactive exploration.

## 2. Installation

```{r}
# From GitHub
# install.packages("remotes")
# remotes::install_github("benben-miao/SeuratVisPro")

library(SeuratVisPro)
library(Seurat)
library(ggplot2)
```

## 3. Shiny App

```r
launchSeuratVisPro()
```

## 4. Usages

### Example Data

```{r SeuratVisProExample}
obj <- SeuratVisProExample(
  n_cells = 300,
  n_genes = 1000,
  n_clusters = 10,
  seed = 123,
  genes_mt = "^MT-",
  neighbor_dims = 10,
  cluster_res = 0.5,
  umap_dims = 10,
  spatial = FALSE
)

Seurat::DimPlot(obj, group.by = "cluster")
```

### VisQCPanel

```{r VisQCPanel}
p <- VisQCPanel(
  obj,
  assay = NULL,
  genes_mt = "^MT-",
  genes_ribo = "^RPL|^RPS",
  group.by = "seurat_clusters",
  interactive = FALSE,
  palette = "C",
  violin_width = 0.8,
  violin_alpha = 0.3,
  box_width = 0.3,
  box_alpha = 0.5
)

p
```

### VisClusterStability

```{r VisClusterStability}
res <- VisClusterStability(
  obj,
  resolution_range = seq(0.2, 1.2, by = 0.2),
  dims = 1:10,
  reps = 5,
  prop = 0.8,
  palette = "C"
)

res$plot
head(res$summary)
```

### VisMarkerAtlas

```{r VisMarkerAtlas}
res <- VisMarkerAtlas(
  obj,
  markers_top = 5,
  logfc_threshold = 0.25,
  min_percent = 0.1,
  test_method = "wilcox",
  palette = "C"
)

res$plot
head(res$markers)
```

### VisBatchAlign

```{r VisBatchAlign}
obj$batch <- sample(c('A','B'), ncol(obj), replace = TRUE)

res <- VisBatchAlign(
  obj,
  batch = 'batch',
  reduction = 'pca',
  dims = 1:10,
  k = 20,
  palette = "C",
  violin_width = 0.8,
  violin_alpha = 0.3,
  box_width = 0.3,
  box_alpha = 0.5
)

res$plot
head(res$summary)
```

### VisGeneTrend

```{r VisGeneTrend}
p <- VisGeneTrend(
  obj,
  features = c("G10", "G20", "G30"),
  by = "pseudotime",
  reduction = "umap",
  dims = 1:2,
  smooth.method = "loess",
  palette = "C",
  point_size = 2,
  point_alpha = 0.3,
  smooth_alpha = 0.3,
  smooth_linewidth = 1.5
)

p
```

### VisLigRec

```{r VisLigRec}
lr <- data.frame(ligand = paste0('G', 1:5), receptor = paste0('G', 6:10))

res <- VisLigRec(
  obj,
  assay = NULL,
  lr_table = lr,
  group.by = "seurat_clusters",
  palette = "C",
  tile_alpha = 0.8
)

res$plot
head(res$scores)
```

### VisClusterTree

```{r VisClusterTree}
p <- VisClusterTree(
  obj,
  assay = NULL,
  group.by = "seurat_clusters",
  dist.metric = "euclidean",
  linkage = "complete",
  show_heatmap = TRUE,
  palette = "C",
  tile_alpha = 0.8
)

p
```

### VisMetaFeature

```{r VisMetaFeature}
sets <- list(SetA = paste0('G', 1:10), SetB = paste0('G', 11:20))

res <- VisMetaFeature(
  obj,
  feature_sets = sets,
  group.by = "seurat_clusters",
  nbin = 24,
  min.size = 3,
  palette = "C",
  violin_width = 0.8,
  violin_alpha = 0.3,
  box_width = 0.3,
  box_alpha = 0.5
)

res$plot
```

### VisCellCycle

```{r}
genes_s <- paste0('G', 1:10)
genes_g2m <- paste0('G', 11:20)

res <- VisCellCycle(
  obj,
  genes_s,
  genes_g2m,
  reduction = "umap",
  dims = 1:10,
  palette = "C",
  alpha = 0.8
)

res$plot
```

### VisEmbeddingContour

```{r VisEmbeddingContour}
p <- VisEmbeddingContour(
  obj,
  group.by = "seurat_clusters",
  reduction = "umap",
  levels = 5,
  palette = "C",
  point_size = 1,
  point_alpha = 0.5,
  contour_alpha = 0.1
)

p
```

### VisGeneCoexpHive

```{r VisGeneCoexpHive}
p <- VisGeneCoexpHive(
  obj,
  genes = paste0("G", 1:100),
  reduction = "pca",
  threshold = 0.2,
  palette = "C",
  point_size = 3,
  point_alpha = 0.8,
  label_size = 3,
  curve_alpha = 0.5
)

p
```

### VisSpatialOverlay

```{r VisSpatialOverlay}
obj_sp <- SeuratVisProExample(n_cells = 300, n_genes = 1000, n_clusters = 10, spatial = TRUE)

p <- VisSpatialOverlay(
  obj_sp,
  features = c("G1", "G2", "G3", "G4"),
  image = NULL,
  coords_cols = c("x", "y"),
  palette = "C",
  point_size = 2,
  alpha = 0.5
)

p
```

### VisHexEntropy

```{r VisHexEntropy}
p <- VisHexEntropy(
  obj,
  group.by = "seurat_clusters",
  reduction = "umap",
  bins = 30,
  palette = "C"
)

p
```

### VisLocalMoran

```{r}
p <- VisLocalMoran(
  obj,
  gene = 'G10',
  reduction = "umap",
  k = 15,
  palette = "C",
  point_size = 2,
  point_alpha = 0.8
)

p
```

### VisClusterFlowGraph

```{r}
p <- VisClusterFlowGraph(
  obj,
  group.by = "seurat_clusters",
  reduction = "umap",
  palette = "C",
  point_size = 7,
  point_alpha = 0.9,
  label_size = 5
)

p
```
